Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-07-11 Paper/paper.tex
Update

From Figure~\ref{fig:mosaic} we see that the distribution of luminosity
function values in each redshift bin are suggestive of a double power
law form for the QLF.  We will fit such a form below. 
However, in several redshift bins we note a suspicious decline of the
luminosity function at the faint limit of several surveys, for example in
the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and $z\sim 4$.
The inconsistency between the SDSS faint end and the deeper
2SLAQ QLF indicates that the SDSS selection function is
systematically overestimated at its magnitude limit.
At $z\sim 4$ the SDSS faint end QLF is inconsistent with the fainter
\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
by eye, discard the contributing quasars from our analysis, and set their
selection function values to zero.
The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by
open circles.

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.  We adopt the
posterior median as our fiducial model fit, and the 68.26\%
equal-tailed credible interval as the uncertainty on $\phi$.
Consistent with previous studies, the double power law model provides
an excellent description of the luminosity function model over almost
the complete range of redshifts spanned by the data.  It is only in
the highest redshift bin ($z=5.5$--$6.5$) that the data seem to favour
a single power law.  In this bin, the resultant posterior distribution
of the break magnitude $M_*$ is bimodal with favoured values at the
faint ($M_*>-18$) and bright end of the data ($M_*<-30$).  While in
the literature $z\sim 6$ quasars have been assumed to lie on the
bright end of the luminosity function
\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
function at lower redshifts ($z<5.5$) suggests that these AGN should
instead be understood to describe the faint-end of a double power law.
As we discuss below, $M_*$ gets progressively brighter with redshift.
Therefore, after inspecting the data at lower redshifts, we use
restricted priors in the $z=5.5$--$6.5$ redshift bin in order to avoid
bimodal distributions.  In this bin, we restrict the bright-end slope
$\alpha$ to values less than $-4$, which is equivalent to forcing
$M_*$ to be at the bright end of the data.  Other parameters continue
to have wide uniform priors.  This also illustrates the importance of
analysing the evolution of the QLF with redshift.

@@

@@

Figure~\ref{fig:mosaic_global}
shows the three
%% JFH global 
models in comparison
with the binned fits from the previous section.  The shaded regions
show the one-sigma (68.26\%) uncertainty.  The symbols show the
luminosity function binned in luminosity and redshift, and the yellow
shaded regions show the posterior distribution of the double power law
luminosity functions in various redshift bins, as in
Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
error are excluded from Figure~\ref{fig:mosaic_global}.  All three
global models are in excellent agreement with the binned models,
although Model~1 performs better.
%% JFH by eye model 1 performs better

Figure~\ref{fig:evoln_global} shows the parameter evolution in the
global models, by comparing it with the results from the fits in
individual redshift bins shown in Figure~\ref{fig:evoln}.  All three
models capture the steepening of the faint end of the luminosity
function towards higher redshifts.  The derived form of Model~1 is
shown by the black curves in Figure~\ref{fig:evoln_global}.  The
accompanying grey shaded area depicts the one-sigma (68.26\%)
uncertainty.  The model is in excellent agreement with the results of
the fits in redshift bins discussed in the previous section.
%% JFH Reference Figure 5 here as well.  
The
deviation of the BOSS quasars at $z=2$--$4$ from the smooth evolution
is again strikingly apparent.  So is
%% JFH , as is the deviation
the deviation of the SDSS and
2SLAQ quasars at $z<0.6$.  This is an indirect justification for the
data selection discussion previously in Section~\ref{sec:bins}.
Unfortunately, this model suffers
%% JFH suffers from 
with a remarkably sharp break in the
evolution of the faint-end slope $\beta$ at about $z\sim 3.5$.  As
seen in Figure~\ref{fig:evoln_global}, the data seem to require this
break, although it seems unlikely that such a sharp break at this
redshift would be physical.  Model 1 thus serves to emphasize the
necessity of better quality data at these redshifts.  Models 2 and 3
are shown in Figure~\ref{fig:evoln_global} by the green and orange
curves, respectively.  The corresponding parameter values are
tabulated in Table~\ref{tab:global}.

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  Similar to Figure~\ref{fig:evoln_global},
symbols show the posterior median values with one-sigma uncertainties from the
double power law fits to the data in redshift bins.
%% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
%% should be able to plot the data on here with Poisson errors in exactly the same way that you do when you compute the binned
%% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
Solid curves and
shaded regions show the global models.  This number density evolution
again highlights the systematic error in data at $z\sim 3$.  The
number density of AGN down to the limit of
%% JFH the deepest spectroscopic surveys 
spectroscopic data
($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$ at its peak.  This
density rapidly increases
%% JFH I think you mean decreases here
at low redshifts and then drops gradually at
high redshifts.  Figure~\ref{fig:rhoqso} also shows the familiar
downsizing feature in which the number density of faint AGN peaks at
lower redshifts than that of the bright AGN.  While the number density
of AGN with $M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN
with $M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at
which spectroscopic data exist, $M_*<-21$, the number density of qsos
peaks at $z\sim 1$.
%% JFH The figure is not consistent with this statement. The model showing M < 21 is peaking
%% just below z = 2. 
However, the difference between our three models
is dramatically evident in Figure~\ref{fig:rhoqso}.  Model~1 prefers a
decrease in the number density of faint quasars at $z\sim 3$ followed
by an increase at higher redshift.  This is caused by the rapid
steepening of the faint-end slope in this model at this redshift.
%% JFH Reference lower right panel of figure 6 here. 
Figure~\ref{fig:rhoqso} reveals another property of these models: when
extrapolated, the AGN number density diverges in all three models at
high redshifts.
%% JFH I think this is just an artifiact of your fitting procedure,
%% i.e. that these polynomial coefficients are unconstrained at really
%% high-z. Do these fits include the banados and MOrtlock quasars? In
%% that case the divergence should not occur, at least for the
%% brightest bin.  Furthermore, if you would make this plot with the
%% data instead of of integrating fits, you would be able to plot
%% those objects on here as well.
This is result of the steep faint-end slope at high
redshifts combined with the rapid brightening of the break luminosity.
While no data exist at redshift $z>7.5$, this divergent behaviour is
shared by previous models in the literature
\citep{2007ApJ...654..731H}.  Figure~\ref{fig:rhoqso} also shows that
although Models 2 and 3 exhibit regular behaviour in the evolution of
the AGN number density at $z\sim 3$, they do not fit the $z\sim
4$--$5$ data as well as Model 1.

@@

%% JFH My main feedback on this section is that you need to elaborate more on which samples you included and excluded and why. That
%% is fine if it is all based on by eye discarding things. We need to make the point more clearly that the various surveys suffer
%% systematics, and hence cannot yet really be combined to give a sensible global evolution without some kind of massaging or choices
%% about which datasets to trust.

@@

%% JFH I think you could possibly break of this last section as a separate letter. The paper above would just be a data analysis and
%% compilation paper.

We now discuss the contribution of AGN to the hydrogen and helium
reionization in our luminosity function model.  We first derive the
redshift evolution of the 912\,\AA\ emissivity of AGN,
and then use this to estimate the contribution of AGN to the \ion{H}{i} photoionization rate
between $z=0$ and $z=7$, as well as the redshift evolution of the average \ion{He}{iii} fraction
in the IGM for a quasar-driven \ion{He}{ii} reionization.
%% JFH Mention low-z UVB here as well in intro.

@@

%% GW simplified the following derivation
%The rate of emission of photons of frequency $\nu$ by quasars can be
%written as
%\begin{equation}
%  \dot n_\nu = \int dM_\nu \phi(M_\nu) \frac{L_\nu(M_\nu)}{h\nu},
%\end{equation}
%where the integral is over a suitable range of magnitudes, the
%monochromatic luminosity $L_\nu(M)$ is related to the (absolute AB)
%magnitude by \citep{1983ApJ...266..713O}
%\begin{equation}
%  M_\nu = -2.5\log_{10}L_\nu+51.60,
%\end{equation}
%and $\phi$ is the luminosity function.  The 912\,\AA\ luminosity is
%related to the UV luminosity at 1450\,\AA\ by Equation~(\ref{eqn:sed})
%or (\ref{eqn:sed_faint})
%\begin{equation}
%  L_{912}=L_{1450}\left(\frac{\nu_{912}}{\nu_{1450}}\right)^{-0.61}=L_{1450}\left(\frac{912}{1450}\right)^{0.61},
%\end{equation}
%depending on the AGN luminosity.  The corresponding comoving volume
%emissivity is
%\begin{equation}
%  \epsilon_\nu = \dot n_\nu h\nu.
%  \label{eqn:epsilon}
%\end{equation}
With our adopted SED the specific comoving volume emissivity of quasars at 912\,\AA\ can be written as
\begin{eqnarray}\nonumber
\epsilon_{912}\left(z\right)&=&\int\limits_{-\infty}^{M_{1450}^\mathrm{lim}}\phi\left(M_{1450},z\right)10^{-0.4\left(M_{1450}-51.60\right)}\,\mathrm{d}M_{1450}\\
& &\times\left(\frac{912}{1450}\right)^{0.61}\quad,
\label{eqn:epsilon}
\end{eqnarray}
which depends on the adopted magnitude limit $M_{1450}^\mathrm{lim}$ and on the
faint-end slope of the QLF if $M_{1450}^\mathrm{lim}\gg M_*$.
The black circles in Figure~\ref{fig:e912_2} show the comoving 912\,\AA\ emissivity
obtained from the individual QLF fits (Table~\ref{tab:bins}) for $M_{1450}<-18$ (left panel)
and $M_{1450}<-21$ (right panel), respectively. Redshift bins that were removed from
the analysis due to large systematic errors in the QLF parameters are shown as open circles.
\textbf{GW: Add a sentence on error bars.}
Our derived emissivity values at 912\,\AA\ and at 1450\,\AA\ are listed in Table~\ref{tab:emissivity_bins}
for reference.
The emissivity peaks between $z=2$ and 3 at $\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
depending on the magnitude limit, and decreases rapidly towards lower and higher redshifts.
Systematic errors in the faint-end slope derived from BOSS data are
more pronounced for $M_{1450}<-18$ due to extrapolation of the QLF.

@@

%% Original text from GK with comments from JFH, rewritten by GW below

%Figure~\ref{fig:e912_2} shows the comoving 912\,\AA\ emissivity when
%the luminosity function is integrated down to $M_{1450}<-21$ (right
%panel) and when it is integrated down to $M_{1450}<-18$ (left panel).
%% JFH Figure 8 is a nightmare to look at. You need to separate this into multiple
%% figures somehow. Perhaps one with curves and one with points. 
%Redshift bins that were removed from analysis due to large systematic
%errors are shown as open circles.  The emissivity peaks at $z=2$--$3$,
%depending on the luminosity integration limit, at
%$\epsilon_{912}=10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}}$
%and decreased
%% JFH decreases 
%rapidly towards high redshifts.  A continuous
%description of this emissivity evolution is valuable in deriving the
%hydrogen photoionizing flux in the IGM.  In principle, the luminosity
%function evolution models discussed in the previous section provide
%such a description.  Unfortunately, as discussed above, all of these
%models suffer from pathologies such as non-monotonic or divergent
%% JFH divergence is just becuase of how you do the fits, and not having data at high-z. I don't think
%% that should be highlighted. 
%AGN
%number densities, likely resulting from residual systematic errors in
%the data.  Therefore, here we describe the emissivity evolution by the
%five-parameter functional form used by \citet{2012ApJ...746..125H}
%\begin{equation}
%  \epsilon_{912}=\epsilon_0(1+z)^a\frac{\exp(-bz)}{\exp(cz)+d}.
%  \label{eqn:e912fit}
%\end{equation}
%We fit this model to the emissivity estimates in the redshift bins,
%shown in Figure~\ref{fig:e912_2}, assuming a Gaussian likelihood for
%the emissivity in each bin.  The resultant best-fit curves and the
%corresponding one-sigma uncertainties are shown in
%Figure~\ref{fig:e912_2} for $M_{1450}<-18$ and $M_{1450}<-21$.  The
%912\,\AA\ emissivities in various redshift bins and in these best-fit
%models are tabulated in Appendix~\ref{sec:tables}.  The best-fit
%form of Equation~\ref{eqn:e912fit} is given by
%\begin{multline}
%  \epsilon_{912}=(10^{24.49}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{7.57}\\\times\frac{\exp(-1.78z)}{\exp(1.01z)+29.20}
%\end{multline}
%for $M_{1450}<-18$, and by 
%\begin{multline}
%  \epsilon_{912}=(10^{24.11}\mathrm{erg\, s^{-1}\, Hz^{-1}\, cMpc^{-3}})(1+z)^{6.64}\\\times\frac{\exp(-0.65z)}{\exp(1.82z)+20.45}
%\end{multline}
%for $M_{1450}<-21$.
%% JFH So if I understand correctly you have given up on the global model and are now doing things
%% with the binned fits, since your global model produces weird non-monotonic behavior. You need to state
%% what you are doing here, so the reader understands where these data points come from on the plot.
%Before proceeding to derive a hydrogen photoionization rate estimate
%from these emissivities, we now comment on the comparison of our
%results with estimates from the literature.  Several of these are
%shown in Figure~\ref{fig:e912_2}.  The brown dashed curve in
%Figure~\ref{fig:e912_2} shows the AGN 912\,\AA\ emissivity model of
%\citet{2012ApJ...746..125H}, which is based on the bolometric
%luminosity function model of \citet{2007ApJ...654..731H}.  Their
%assumed emissivity agrees reasonably well with our $M_{1450}<-21$
%case, although at its maximum the emissivity in the
%\citet{2007ApJ...654..731H} model is lower by about 20\%.  The
%differences between the two models are much larger for $M_{1450}<-18$.
%Figure~\ref{fig:e912_2} also shows the model presented by
%\citet{2015ApJ...813L...8M}.  This model disagrees with ours rather
%severely at almost all redshifts in the range considered here, for
%both of our integration limits.  It is important to note here that a
%direct comparison of our model with \citet{2012ApJ...746..125H} and
%\citet{2015ApJ...813L...8M} is difficult because these models
%integrate the luminosity function to a fixed fraction of the break
%luminosity $L_*$ instead of a fixed absolute magnitude.  The chosen
%limite
%% JFH limite --> limit 
%by \citet{2012ApJ...746..125H} and \citet{2015ApJ...813L...8M}
%is $0.01L_*$.  Using a limit that depends on the break luminosity is
%problematic as different quasar surveys used to develop these
%emissivity models often report strikingly different break luminosity
%values.  Even when these samples are homogeneized appropriately, have
%% JFH adopting such an integratino limit....
%such an integration limit is likely only justified if the faint-end
%slope of the luminosity function is sufficiently shallow.  This issue
%also affects some other models in the literature, such as those
%presented by \citet{2015AA...578A..83G}, \citet{2015MNRAS.451L..30K}
%and \citet{2018arXiv180104931P}.
%\citet{2017MNRAS.466.1160M} integrated the luminosity function down to
%$M_{1450}=-19$.  However, their model strongly disagrees with our
%inference, as seen in Figure~\ref{fig:e912_2}, potentially due to
%biases resulting from inhomogeneously combining binned luminosity
%function estimates from different data sets.  The emissivity
%determinations from the luminosity function derived from a
%variability-selected sample observed using the Sloan
%% JFH Sloan telescopee --> SDSS telescope
%telescope and the
%Multiple Mirror Telescope (MMT) by \citet{2013A&A...551A..29P} is in
%agreement with our $M_{1450}<-21$ determination for $z<2.2$.  At other
%redshifts and for $M_{1450}<-18$, the models disagree by 10--30\%.
%%% GW: At z>2.2 the disagreement is much larger than 10-30 percent!!!
%The sample of 1877 quasars presented by \citet{2013A&A...551A..29P} is
%not included in our analysis, and therefore provides a cross-check.
%(This sample also does not overlap with the variability-selected
%sample reported by the BOSS survey \citep{2013ApJ...773...14R}.)
%\citet{2013A&A...551A..29P} assume constant double power law
%luminosity function slopes with a break at $z=2.2$ and assume a pure
%luminosity evolution.  This leads to a discontinuity in the emissivity
%evolution in their model at $z=2.2$.  In Figure~\ref{fig:e912_2}, we
%convert their $g$-band magnitudes to $M_{1450}$ and integrate the
%resultant luminosity function down to our two chosen integration
%limits with our chosen SED for a direct comparison.
%Figure~\ref{fig:e912_2} also shows the model presented by
%\citet{2016A&A...587A..41P}.  We consider their PLE$+$LEDE model, in
%which the faint-end slope is assumed to stay constant with redshift.
%Although the emissivity evolution in this model is continuous at
%$z=2.2$, unlike in the \citet{2013A&A...551A..29P} model, it is not
%smooth.  This model agrees with our $M_{1450}<-18$ result to a better
%degree relative to the \citet{2013A&A...551A..29P} model, bjt
%% JFH bjt --> but
%it results in a higher emissivity in the $M_{1450}<-21$ case.
%\citet{2017A&A...608A..64C} reanalysed the \citet{2016A&A...587A..41P}
%sample with an improved $K$-correction implementation, but, as seen in
%Figure~\ref{fig:e912_2}, their estimate is higher by 50\% or more
%throughout the redshift range of their data.
%% JFH For the Palanque and Caditz etc. comparisons, it occurs to me that these guys
%% probably used the luminosity function and not the epsilon_912. I'm just wondering why you
%% choose to do the comparisons in this quantity if other authors didn't compute this quantity. I understand
%% that one is the integral of the other, but it would seem more sensible to me to compare to the Palangue-luminosity
%% function when you discuss the individual fits to luminosity functions in say their same redshift bins, then when you
%% compute the emissivity evolution here. This just seems out of place. I think comparing to other peoples emissivities
%% here is sensible, but integrating other peoples lum functions here is less transparent.

%At higher redshifts, \citet{2017ApJ...847L..15O} recently fit a double
%power law luminosity function model to a combined binned samples of
%\citet{2016ApJ...833..222J}, \citet{2010AJ....139..906W}, and
%\citet{2015ApJ...798...28K}, and an X-ray-selected AGN candidate with
%photometric redshift $z\sim 6$ reported by
%\citet{2018MNRAS.474.2904P}.  We show the resultant
%912\,\AA\ emissivity by a rectangle in Figure~\ref{fig:e912_2}.  The
%lower side of the rectangle corresponds to the emissivity for the
%\citet{2017ApJ...847L..15O} model excluding the
%\citet{2018MNRAS.474.2904P} AGN.  When this AGN candidate is included,
%the emissivity is higher; this is shown by the upper end of the
%rectangle.  Our emissivities broadly in agreement with the
%determination of \citet{2017ApJ...847L..15O}.  Figure~\ref{fig:e912_2}
%shows the determination from the fits of \citet{2015AA...578A..83G}.
%These authors also choose a break luminosity-dependent integration
%limit of $0.01L_*$, which corresponds to $M_{1450}\sim -18$ in their
%model.  The resultant emissivities are factors of 2 to 3 higher than
%our determinations for $z=4$--$6$ for $M_{1450}<-21$.  This is
%puzzling at first sight, because the AGN candidates reported by
%\citet{2015AA...578A..83G} are consistent with our luminosity function
%estimates obtained without these candidates (see
%Appendix~\ref{sec:conv}).  Our luminosity function are also somewhat
%steeper than those reported by \citet{2015AA...578A..83G}.  The
%discrepancy is explained by the difference in the two luminosity
%function models at intermediate magnitudes.  We find that the data
%prefer a much brighter break luminosity than that inferred by
%\citet{2015AA...578A..83G}.  This reduces our emissivities relative to
%their estimates.  We go into this issue in further detail in
%Appendix~\ref{sec:conv}.

%\citet{2018AJ....155..131M} recently extended their previous Stripe~82
%AGN sample by 1.5 magnitude and fit a double power law luminosity
%function model to a combined SDSS $+$ Stripe~82 $+$ CFHTLS sample at
%$4.7 < z < 5.1$.  These authors fixed the bright-end slope to
%$\alpha=-4$ and obtained a shallower faint-end slope ($\beta=-1.97$)
%than our models at this redshift ($\beta\sim -2.3$).  Rescaling their
%LF to our cosmology and assuming our SED result in the emissivities
%shown in Figure~\ref{fig:e912_2}.  Our emissivity agrees with the
%measurement of \citet{2018AJ....155..131M} for $M_{1450}<-21$ but is
%higher than their measurement for $M_{1450}<-18$, which is not
%surprising due to the difference in the luminosity function slopes.
%The emissivity derived from the luminosity function of
%\citet{2018PASJ...70S..34A} is also shown in Figure~\ref{fig:e912_2}.
%These authors report 1668 AGN candidates at $3.5<z<4.3$, of which 76
%have spectroscopic redshifts.  Their reported faint-end slope is very
%flat ($\beta=-1.3\pm 0.05$), inconsistent with our determination at
%all redshifts.  Their inferred emissivity is consistent with our
%estimate for $M_{1450}< -21$.  Their emissivity does not change
%significantly with the integration limit due to the shallow faint-end
%slope.  As a result, our $M_{1450}< -18$ determination of the
%emissivity is considerably higher than their estimate.  We also
%compare our emissivities with the determinations reported by
%\citet{2012ApJ...755..169M} at $z\sim 3.2$ and $z\sim 4$.  Their
%emissivity in reasonable agreement with our model for $M_{1450}<-21$
%at $z\sim 3.2$.  Our emissivity estimates are in good agreement with
%recent estimates of \citet{2018MNRAS.474.2904P} at $z=4$--$5$.

%At low redshifts, \citet{2009A&A...507..781S} combined data from the
%Hamburg/ESO survey and the SDSS to measure a quasar luminosity
%function at $z=0$ in their $B_J$ band to minimize host galaxy
%contribution.  We convert their $B_J$ magnitudes (Vega system) to
%$M_{1450}$ (AB) as
%\begin{equation}
%  M_{1450,\mathrm{AB}}=M_{B_J, \mathrm{Vega}}+0.59.  
%\end{equation}
%In this magnitude system, the luminosity function reported by
%\citet{2009A&A...507..781S} has a very faint break luminosity of
%$M_*=-18.87$.  The faint-end slope is also steep ($\beta=-2$).  We
%integrate this luminosity function down to our limiting magnitudes of
%$M_{1450}=-18$ and $-21$.  The resultant values are shown in
%Figure~\ref{fig:e912_2}.  Our emissivity values at $z=0$ lie in
%between the \citet{2009A&A...507..781S} measurements.  The convergence
%in the emissivity is slower in their measurements than in our models
%because of the shallower faint-end slope at this redshift in our model
%($\beta\sim -1.22$).

@@

%The 912\,\AA\ emissivity can now be used to calculate the hydrogen
%ionizing flux and the hydrogen photoionization rate contributed by
%AGN.  This adds an additional layer of uncertainty as the \HI\ column
%density structure of the IGM has not been measured at all redshifts of
%interests, thereby requiring uncertain extrapolation.  The frequency
%dependence of the AGN SED above 1~Ry is given by
%Equation~(\ref{eqn:sed}) or (\ref{eqn:sed_faint}), so that for $\nu >
%\nu_{912}$
%\begin{equation}
%  \epsilon_\nu = \epsilon_{912}\left(\frac{\nu}{\nu_{912}}\right)^\alpha,
%  \label{eqn:epsilon_freq}
%\end{equation}
%where $\alpha=-1.70$ (Equation~\ref{eqn:sed}) or $-0.56$
%(Equation~\ref{eqn:sed_faint}).  We assume that faint AGN
%($M_{1450}>-23$) have the shallower spectral slope.  The flux in the
%IGM is written as a solution of the cosmological radiative transfer
%equation as \citep{2012ApJ...746..125H}
%\begin{multline}
%  j(\nu_0, z_0)=\frac{1}{4\pi}\int_{z_0}^\infty dz\frac{dl}{dz}
%  \frac{(1+z_0)^3}{(1+z)^3}\epsilon(\nu,z)\\
%  \times\exp{(-\tau_\mathrm{eff}(\nu_0, z_0, z))},
%  \label{eqn:flux}
%\end{multline}
%where
%\begin{equation}
%  \nu = \nu_0\left(\frac{1+z}{1+z_0}\right).
%\end{equation}
%Here the effective optical depth is estimated as
%\begin{equation}
%  \tau_\mathrm{eff}(\nu_0, z_0, z) = \int_{z_0}^z dz^\prime\int_0^\infty
%  dN_\mathrm{HI} f(N_\mathrm{HI}, z^\prime) (1-e^{-\tau_\nu}),
%\end{equation}
%where $\tau_\nu=\sigma_\nu N_\mathrm{HI}$.  (We ignore the small
%contribution of helium to the opacity.)  We assume the \HI\ column
%density distribution given by \citet{2012ApJ...746..125H}.
%% JFH elaborate on this. Say it is chosen to reproduce Worseck's MFP measurements
%% and that it sensible extrapolate or something. You need to make it clear that it is indeed
%% Gabors MFP that you are using here. 
%The
%\HI\ photoionization rate is then given by
%\begin{equation}
 % \Gamma_\mathrm{HI}=\int_{\nu_{912}}^\infty d\nu
 % \frac{4\pi j(\nu,z)}{h\nu} \sigma(\nu),
%\end{equation}
%where $\sigma$ is the photoionization cross-section.
%% JFH Is it obvious that the uncertaintites in the MFP which propagate into the HM fit for the column density
%% distribution do not matter? If so this needs to be explicitly stated.

@@

%% This is the previous version of this section, now changed by GW
%We have presented an analysis of the evolution of the UV luminosity
%function of AGN from redshift $z=0$ to $7.5$ using a combined sample
%of close to 85,000 colour-selected AGN from 12 data sets, homogenized
%with respect to the assumed cosmology, intrinsic AGN spectrum, and the
%magnitude system.  AGN from 11 of these 12 samples have reported
%spectroscopic redshifts, and all but two AGN have known completeness
%estimates.  These data span magnitudes down to $M_{1450}=-22$ at high
%redshifts ($z\gtrsim 3.5$).

>>>>

From Figure~\ref{fig:mosaic} we see that the distribution of luminosity
function values in each redshift bin are suggestive of a double power
law form for the QLF.  We will fit such a form below. 
However, in several redshift bins we note a suspicious decline of the
luminosity function at the faint limit of several surveys, for example in
the 2SLAQ sample at $z<2.2$, and in the SDSS sample at $z<1.8$ and $z\sim 4$.
The inconsistency between the SDSS faint end and the deeper
2SLAQ QLF indicates that the SDSS selection function is
systematically overestimated at its magnitude limit.
At $z\sim 4$ the SDSS faint end QLF is inconsistent with the fainter
\citet{2011ApJ...728L..26G} QLF. We identify such discrepant bins
`by eye', discard the contributing quasars from our analysis, and set their
selection function values to zero.
The discarded magnitude bins are shown in Figure~\ref{fig:mosaic} by
open circles.

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.  We adopt the
posterior median as our fiducial model fit, and the 68.26\%
equal-tailed credible interval as the uncertainty on $\phi$.  The
resultant parameter values are listed in Table~\ref{tab:bins}.
Consistent with previous studies, the double power law model provides
an excellent description of the luminosity function model over almost
the complete range of redshifts spanned by the data.  It is only in
the highest redshift bin ($z=5.5$--$6.5$) that the data seem to favour
a single power law.  In this bin, the resultant posterior distribution
of the break magnitude $M_*$ is bimodal with favoured values at the
faint ($M_*>-18$) and bright end of the data ($M_*<-30$).  While in
the literature $z\sim 6$ quasars have been assumed to lie on the
bright end of the luminosity function
\citep[e.g.,][]{2016ApJ...833..222J}, a comparison with the luminosity
function at lower redshifts ($z<5.5$) suggests that these AGN should
instead be understood to describe the faint-end of a double power law.
As we discuss below, $M_*$ gets progressively brighter with redshift.
Therefore, after inspecting the data at lower redshifts, we use
restricted priors in the $z=5.5$--$6.5$ redshift bin in order to avoid
bimodal distributions.  In this bin, we restrict the bright-end slope
$\alpha$ to values less than $-4$, which is equivalent to forcing
$M_*$ to be at the bright end of the data.  Other parameters continue
to have wide uniform priors.  This also illustrates the importance of
analysing the evolution of the QLF with redshift.

@@

%% Bins considered
%% to be dominated by systematics are marked in Table~\ref{tab:bins}.
%% These bins should be avoided while evaluating the evolution of the
%% luminosity function.  The remaining redshift can

@@

Figure~\ref{fig:mosaic_global} shows the three global models in
comparison with the binned fits from the previous section.  The shaded
regions show the one-sigma (68.26\%) uncertainty.  The symbols show
the luminosity function binned in luminosity and redshift, and the
yellow shaded regions show the posterior distribution of the double
power law luminosity functions in various redshift bins, as in
Figure~\ref{fig:mosaic}.  Bins containing data with large systematic
error are excluded from Figure~\ref{fig:mosaic_global}.  All three
global models are in excellent agreement with the binned models,
although Model~1 performs better.

Figure~\ref{fig:evoln_global} shows the parameter evolution in the
global models, by comparing it with the results from the fits in
individual redshift bins shown in Figure~\ref{fig:evoln}.  All three
models capture the steepening of the faint end of the luminosity
function towards higher redshifts.  The derived form of Model~1 is
shown by the black curves in Figure~\ref{fig:evoln_global}.  The
accompanying grey shaded area depicts the one-sigma (68.26\%)
uncertainty.  The model is in excellent agreement with the results of
the fits in redshift bins discussed in the previous section.
The deviation of the BOSS quasars at $z=2$--$4$ from the smooth
evolution is again strikingly apparent, as is the deviation of the
SDSS and 2SLAQ quasars at $z<0.6$.  This is an indirect justification
for the data selection discussion previously in
Section~\ref{sec:bins}.  Unfortunately, this model suffers from a
remarkably sharp break in the evolution of the faint-end slope $\beta$
at about $z\sim 3.5$.  As seen in Figure~\ref{fig:evoln_global}, the
data seem to require this break, although it seems unlikely that such
a sharp break at this redshift would be physical.  Model 1 thus serves
to emphasize the necessity of better quality data at these redshifts.
Models 2 and 3 are shown in Figure~\ref{fig:evoln_global} by the green
and orange curves, respectively.  The corresponding parameter values
are tabulated in Table~\ref{tab:global}.

The evolution of the comoving number density of quasars is shown in
Figure~\ref{fig:rhoqso} when the luminosity function is integrated
down to different limits.  Similar to Figure~\ref{fig:evoln_global},
symbols show the posterior median values with one-sigma uncertainties
from the double power law fits to the data in redshift bins.
%% JFH I'm bothered by the fact that the symbols and error bars here arise from the parametric fits. In my opinion, you
%% should be able to plot the data on here with Poisson errors in exactly the same way that you do when you compute the binned
%% luminosity function data points? These symbols with errors should be the data to me, and not the result of your fitting procedure. 
Solid curves and shaded regions show the global models.  This number
density evolution again highlights the systematic error in data at
$z\sim 3$.  The number density of AGN down to the limit of the deepest
spectroscopic surveys ($M_{1450}<-21$) is about $10^{-5}$ cMpc$^{-3}$
at its peak.  This density rapidly increases with redshift at low
redshifts and then drops with redshift gradually at high redshifts.
Figure~\ref{fig:rhoqso} also shows the familiar downsizing feature in
which the number density of faint AGN peaks at lower redshifts than
that of the bright AGN.  While the number density of AGN with
$M_*<-27$ peaks at $z\sim 2.5$, the number density of AGN with
$M_*<-24$ peaks at $z\sim 2$.  At the faintest luminosity at which
spectroscopic data exist, $M_*<-21$, the number density of qsos peaks
at a slightly lower redshift.  However, the difference between our
three models is dramatically evident in Figure~\ref{fig:rhoqso}.
Model~1 prefers a decrease in the number density of faint quasars at
$z\sim 3$ followed by an increase at higher redshift.  This is caused
by the rapid steepening of the faint-end slope in this model at this
redshift (Figure~\ref{fig:evoln_global}).  Figure~\ref{fig:rhoqso}
reveals another property of these models: when extrapolated, the AGN
number density diverges in all three models at high redshifts.
%% JFH I think this is just an artifiact of your fitting procedure,
%% i.e. that these polynomial coefficients are unconstrained at really
%% high-z. Do these fits include the banados and MOrtlock quasars? In
%% that case the divergence should not occur, at least for the
%% brightest bin.  Furthermore, if you would make this plot with the
%% data instead of of integrating fits, you would be able to plot
%% those objects on here as well.
This is result of the steep faint-end slope at high
redshifts combined with the rapid brightening of the break luminosity.
While no data exist at redshift $z>7.5$, this divergent behaviour is
shared by previous models in the literature
\citep{2007ApJ...654..731H}.  Figure~\ref{fig:rhoqso} also shows that
although Models 2 and 3 exhibit regular behaviour in the evolution of
the AGN number density at $z\sim 3$, they do not fit the $z\sim
4$--$5$ data as well as Model 1.

@@

@@

We now discuss the contribution of AGN to the hydrogen and helium
reionization in our luminosity function model.  We first derive the
redshift evolution of the 912\,\AA\ emissivity of AGN, and then use
this to estimate the contribution of AGN to the \ion{H}{i}
photoionization rate between $z=0$ and $z=7$, as well as the redshift
evolution of the average \ion{He}{iii} fraction in the IGM for a
quasar-driven \ion{He}{ii} reionization.

@@

With our adopted SED the specific comoving volume emissivity of
quasars at 912\,\AA\ can be written as
\begin{eqnarray}\nonumber
\epsilon_{912}\left(z\right)&=&\int\limits_{-\infty}^{M_{1450}^\mathrm{lim}}\phi\left(M_{1450},z\right)10^{-0.4\left(M_{1450}-51.60\right)}\,\mathrm{d}M_{1450}\\
& &\times\left(\frac{912}{1450}\right)^{0.61}\quad,
\label{eqn:epsilon}
\end{eqnarray}
which depends on the adopted magnitude limit $M_{1450}^\mathrm{lim}$
and on the faint-end slope of the QLF if $M_{1450}^\mathrm{lim}\gg
M_*$.  The black circles in Figure~\ref{fig:e912_2} show the comoving
912\,\AA\ emissivity obtained from the individual QLF fits
(Table~\ref{tab:bins}) for $M_{1450}<-18$ (left panel) and
$M_{1450}<-21$ (right panel), respectively. Redshift bins that were
removed from the analysis due to large systematic errors in the QLF
parameters are shown as open circles.  \textbf{GW: Add a sentence on
  error bars.}  Our derived emissivity values at 912\,\AA\ and at
1450\,\AA\ are listed in Table~\ref{tab:emissivity_bins} for
reference.  The emissivity peaks between $z=2$ and 3 at
$\epsilon_{912}\simeq 10^{25}\,\mathrm{erg\, s^{-1}\, Hz^{-1}\,
  cMpc^{-3}}$ depending on the magnitude limit, and decreases rapidly
towards lower and higher redshifts.  Systematic errors in the
faint-end slope derived from BOSS data are more pronounced for
$M_{1450}<-18$ due to extrapolation of the QLF.

@@

@@

@@
